\documentclass{anmt}
\newcommand{\ky}{\charname{KYLIE}}
\newcommand{\sh}{\charname{SHANE}}
\begin{document}
\act
\scene
\init{KYLIE and SHANE sit at an outdoor table at a Fatburger. SHANE devours a huge double-patty baconburger, sloppily. KYLIE is doing her best not to de appalled, as she delicately eats her veggieburger.}

\ky
O-k-kay, so we’ve established you and bacon....

\sh
\aside{mouth full}
I know! You don’t know what you’re missing! You’re on a blind date at Fatburger only to get a veggie thing!?

\ky
Yeah, silly me. So. So, what do you do? What’s your job?

\sh
I mean, it’s dripping down my elbows.

\stagedir{SHE looks at his elbows. SHE reaches for a napkin, but decides not to intervene.}

\ky
Yes it is. And your job. You got a commute?

\sh
Two patties! It's like, twice the beef.

\ky
It's exactly twice the beef, yes.

\sh
I don't know which I like better, the beef or the bacon.

\ky
Well, fortunately you got 'em both together, so you don't have to decide. Speaking of deciding, do you have decisions you have to make at work? What do you do? I'm asking you, what do you do?

\sh
And they do something with the cheese. God, it's good. C'mon, forget the veggie thing. Lemme buy you some beef!

\ky
No, I'm good.

\sh
Hot beef. Bacon. I could eat like three of these.

\stagedir{KYLIE takes a bite of her veggieburger; SHANE continues to ravage his burger.}

\begin{song}
\ky
\begin{lyrics}
    \stanza{
        if life were a musical\\
        i could hear what he is thinking.\\
        he'd sing his inner thoughts\\
        while he's chewing and drinking.\\
    }
    \stanza{
        if life were a musical\\
        even though his words are brief,\\
        i'd know his inner thoughts\\
        were more than "burger bacon beef."\\
    }
    \begin{lyrics}
        \stanza{
            i wish i could say it's a record:\\
            three minutes to judge a blind date,\\
            but already i know it's time now to go.\\
            here's someone i could learn to hate.\\
        }
    \end{lyrics}
    \stanza{
        if life were a musical\\
        then his subtext would be clear.\\
        he'd dance his inner thoughts\\
        to a click track in his ear.\\
    }
\end{lyrics}
\end{song}

\stagedir{KYLIE dabs at her salad. SHANE is still gorging on his burger.}

\ky
So if I were to offer to buy you a salad, would you eat it? What're you thinking in that head of yours, Shane? Salad for your thoughts.

\stagedir{We hear Shane's thoughts as he eats his burger. KYLIE stares at Shane.}

\begin{song}
    \charname{SHANE (V.O., via speakers)}
    \aside{his mouth full, even in his thoughts}
    \begin{lyrics}
            \stanza{
                murgg murgg burger burger!\\
                skip the lettuce leaf.\\
                god. tasty. hot burger.\\
                bacon. chees. and beef.
            }
            \begin{lyrics}
                \stanza{
                    god she's hot!\\
                    how can i get her --
                }
            \end{lyrics}
            \stanza{
                murgg murgg burger burger\\
                boxer shorts, not brief.\\
                condom. condom. burger. burger.\\
                bacon. chees. and beef.
            }
            \begin{lyrics}
                \stanza{
                    sex.\\
                    sex.\\
                    bacon. cheese.\\
                    sex.\\
                    sex.\\
                    please.
                }
            \end{lyrics}
            \stanza{
                murgg murgg burger burger\\
                hot beyond belief.\\
                tasty bun. nearly done with my\\
                bacon. cheese. and beef!\\
            }
    \end{lyrics}
    \stagedir{KYLIE gets up and walks away, done with him.}
    \sh
    What? What I say?
    \stagedir{Lights shift to:}
\end{song}

\scene
\init{Griffith Park Observatory. KYLIE and JEROD have brought an old-fashioned picnic basket; they're eating on a blanket on the lawn in front of the observatory.}

\end{document}