\scene
\init{KYLIE and SHANE sit at an outdoor table at a Fatburger. SHANE devours a huge double-patty baconburger, sloppily. KYLIE is doing her best not to de appalled, as she delicately eats her veggieburger.}

\ky
O-k-kay, so we’ve established you and bacon....

\sh
\aside{mouth full}
I know! You don’t know what you’re missing! You’re on a blind date at Fatburger only to get a veggie thing!?

\ky
Yeah, silly me. So. So, what do you do? What’s your job?

\sh
I mean, it’s dripping down my elbows.

\stagedir{SHE looks at his elbows. SHE reaches for a napkin, but decides not to intervene.}

\ky
Yes it is. And your job. You got a commute?

\sh
Two patties! It's like, twice the beef.

\ky
It's exactly twice the beef, yes.

\sh
I don't know which I like better, the beef or the bacon.

\ky
Well, fortunately you got 'em both together, so you don't have to decide. Speaking of deciding, do you have decisions you have to make at work? What do you do? I'm asking you, what do you do?

\sh
And they do something with the cheese. God, it's good. C'mon, forget the veggie thing. Lemme buy you some beef!

\ky
No, I'm good.

\sh
Hot beef. Bacon. I could eat like three of these.

\stagedir{KYLIE takes a bite of her veggieburger; SHANE continues to ravage his burger. \textbf{1. If Life were a Musical.}}

\input{lyrics/1_if_life}

\stagedir{KYLIE dabs at her salad. SHANE is still gorging on his burger.}

\ky
So if I were to offer to buy you a salad, would you eat it? What're you thinking in that head of yours, Shane? Salad for your thoughts.

\stagedir{We hear Shane's thoughts as he eats his burger. KYLIE stares at Shane. \textbf{2. Bacon, Cheese and Beef.}}

\input{lyrics/2_bacon_cheese}
