\scene
\init{Griffith Park Observatory. KYLIE and JEROD have brought an old-fashioned picnic basket; they're eating on a blanket on the lawn in front of the observatory.}

\je
Fascinating you do spectral analysis on cosmetics.

\ky
Wow.  You got all that just from what I said?

\je
Yeah.  I just never thought about the public health issues
involved.  But, duh, you’re applying chemicals right onto your
skin which is semi-porous, so.  It only makes sense.

\ky
\aside{swallows; then:}
And you, what do you do?

\je
It’s kind of technical, but you’re a chemist you’ll probably understand.

\ky
Technically, I’m not a chemist.  I’m an analyst.

\je
Uh-oh.  So you’re going to analyze me?

\ky
I’m already analyzing you.  But don’t worry, I charge only four hundred bucks an hour.

\stagedir{As stupid as these jokes are, they’re genuine, and the two laugh with each other. It's very pleasant and easy.}

\je
Then I’d better start talking.  I work at JPL.

\ky
\aside{impressed}
Jet Propulsion Laboratory?

\je
Yeah.  I’m working on an oxygenation design for the Mars mission.

\ky
Shut up.

\je
Yeah. Like ‘‘The Martian,’’ only real. We launch in four years. The idea is to convert the CO2 in Mars’s atmosphere to oxygen, so we don’t have to take oxygen with us on our way out. The way I explain it to my kids --

\ky
Kids?

\je
I volunteer at an at-risk after school program.  I have about a dozen kids I think I’m really helping change their lives.  It makes me feel good to --

\stagedir{HE continues to speak, but instead of his dialogue, we hear Kylie’s thoughts. \textbf{3. Is He the One?}}

\input{lyrics/3_is_he}

\ky
When you say ‘‘new Republicans,’’ you don’t mean, as in the political party?

\je
Uh, yeah.  I’m a recruiter.

\ky
\aside{picking up her phone}
Omigod, I so forgot!  I have a...I have a --

\stagedir{JEROD watches KYLIE fumbling with her phone and her purse then packing up the picnic. \textbf{4. This Will Never Work.}}

\input{lyrics/4_this_will}
\stagedir{And she's gone. JEROD pulls out his phone and begins texting someone. \textbf{5. Texting Underscore.}}

\underscoring

\stagedir{JEROD huddles over his phone, fascinated by it. He reads aloud what he's texting.}
\je
turns out i'm free 2nite after all where u at?

\stagedir{Lights shift to:}