\scene
\init{Outdoors at the Getty Museum, KYLIE sips at an expensive cup of coffee, along with bright, chipper WHIT.}

\ky
So, Whit.

\wh
Uh-oh.

\ky
Really?

\wh
It’s just --

\ky
I know that uh-oh.  Look, you’re my best friend....

\wh
Oh, this is getting worse and worse.

\ky
Let me get this out.  We’ve been like brother and sister since we were in diapers together, and I really really appreciate your setting me up with both of those blind dates and all.

\wh
But.

\ky
But it’s like you don’t know me at all.  The first guy was a complete carnivore -- all he could talk about was this burger he was eating.

\wh
Oh, crap, you mean Shane.  I forgot that about him and meat.

\ky
Is that his name?  He never even got that far.  And the other guy was a Republican.

\wh
Omigod, no.  Jerod’s a closeted Republican!  Who knew.  I thought you guys would get along.  So, okay, give me another chance to set up some more dates.

\ky
I don’t know, Whit.

\wh
Kylie, I’m sorry about missing the mark.

\ky
Twice.

\wh
But I only want to help you.  You’ve been off the market for like eighteen months.

\ky
Twenty-two.

\wh
There’s someone out there for you, Kylie.  Give me one more chance to find him for you.  C’mon, your ideal guy, what’s he like?

\ky
Well.  Someone who’s just as much into \underline{me} as himself.  Picks up the check, but lets me do it too sometimes without any weirdness. Not a carnivore, and definitely not a Republican.  Someone about your height and build, about your age.  You got a brother, Whit?

\stagedir{WHIT looks at the audience. \textbf{6. Right Before Your Eyes.}}

\include{lyrics/6_right_before}
